Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID

### 2024-01-25 outputs/paper/paper.qmd
paper update

cleaned_branch_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/00-cleaned_branch_data.csv",
    show_col_types = FALSE
  )

cleaned_circulation_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/01-cleaned_circulation_data.csv",
    show_col_types = FALSE
  )

cleaned_visits_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/02-cleaned_visits_data.csv",
    show_col_types = FALSE
  )

branch_circulation_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/03-annual_circulation_by_ward_data.csv",
    show_col_types = FALSE
  )

annual_circulation_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/04-annual_circulation_data.csv",
    show_col_types = FALSE
  )

branch_visits_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/05-annual_visits_by_ward_data.csv",
    show_col_types = FALSE
  )

annual_visits_data <-
  read_csv(
    file = "~/tplactivityanalysis/outputs/data/06-annual_visits_data.csv",
    show_col_types = FALSE
  )
```

>>>>

cleaned_branch_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/00-cleaned_branch_data.csv",
    show_col_types = FALSE
  )

cleaned_circulation_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/01-cleaned_circulation_data.csv",
    show_col_types = FALSE
  )

cleaned_visits_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/02-cleaned_visits_data.csv",
    show_col_types = FALSE
  )

branch_circulation_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/03-annual_circulation_by_ward_data.csv",
    show_col_types = FALSE
  )

annual_circulation_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/04-annual_circulation_data.csv",
    show_col_types = FALSE
  )

branch_visits_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/05-annual_visits_by_ward_data.csv",
    show_col_types = FALSE
  )

annual_visits_data <-
  read_csv(
    file = "~/tpl_activity_analysis/outputs/data/06-annual_visits_data.csv",
    show_col_types = FALSE
  )
```
